CRUSE to Safe Cycling in Ireland

### 2023-09-25 paper.qmd
Fix up footnotes

Uptake of cycling, the main topic of this paper, should be seen in this broader context of transport decarbonisation [@brand2020] and sustainable mobility [@burns2013].
Although cycling uptake appears on the surface to only relate to the 'shift' part of the ASI framework, closer consideration of the knock-on impacts of cycling uptake shows that it can also help avoid unnecessary trips [@nello-deakin2020].
The rapid uptake of highly efficient e-bikes can also be seen as an improvement on most electric vehicles, which are too heavy and expensive to be a sustainable alternative and could in fact delay the transition away from car dependency and inadvertently enable "high travel lock-in" [@anable2019].
At the European level, the European Union has a target of reducing greenhouse gas emissions by 55% by 2030, compared to 1990 levels, and to achieve 'net-zero' by 2050.\[\^1\]

@@

In Ireland, the Road Safety Authority (RSA) has set the target of halving the number of road traffic deaths and serious injuries by 2030.\[\^3\] Doing so while simultaneously enabling rapid uptake of active modes will require key active travel routes to be identified and improved.

>>>>

Uptake of cycling, the main topic of this paper, should be seen in this broader context of transport decarbonisation [@brand2020] and sustainable mobility [@burns2013].
Although cycling uptake appears on the surface to only relate to the 'shift' part of the ASI framework, closer consideration of the knock-on impacts of cycling uptake shows that it can also help avoid unnecessary trips [@nello-deakin2020].
The rapid uptake of highly efficient e-bikes can also be seen as an improvement on most electric vehicles, which are too heavy and expensive to be a sustainable alternative and could in fact delay the transition away from car dependency and inadvertently enable "high travel lock-in" [@anable2019].
At the European level, the European Union has a target of reducing greenhouse gas emissions by 55% by 2030, compared to 1990 levels, and to achieve 'net-zero' by 2050.[^1]

@@

In Ireland, the Road Safety Authority (RSA) has set the target of halving the number of road traffic deaths and serious injuries by 2030.[^3] Doing so while simultaneously enabling rapid uptake of active modes will require key active travel routes to be identified and improved.
